---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rsk

<!-- badges: start -->
<!-- badges: end -->

The goal of rsk is to facilitate fast reading of pressure and temperature RBR files. This package is in the beginning of development stages.

Steps:

1. read SQLite3 database tables (*.rsk)
1. check date times
1. convert binary data (*downloads* table) to millivolt 
1. apply basic calibration parameters
1. apply temperature compensation for pressure


## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jkennel/rsk")
```

## Example


```{r}

library(rsk)
fn  <- '/home/jonathankennel/Storage/data/rbr/rd45a 081871_20191118_1213.rsk'

# this reads in the data
rbr <- Rsk$new(file_name = fn)
```


##  Data
The data is stored in a single dataset in wide format. *raw* refers to the millivolt measurements. For newer duets, temperature is measured onboard and at the sensor tip. *pressure_dbar_comp* refers to the final temperature compensated pressure.

```{r}
rbr$data
```


##  Plot of channels

```{r, eval = FALSE}
rbr$glance()
```

