---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# rsk

<!-- badges: start -->
<!-- badges: end -->

The goal of rsk is to facilitate fast reading of pressure and temperature RBR files. This package is in development and exploration stage as it is accessing a binary table of the .rsk file and the format may change in the future. I am not associated with RBR Ltd., and the focus of this package has been on the compact solo and duet devices for pressure and temperature. If you need a more stable reader for RBR files you may find the *oce* package more useful.

Steps:

1. read SQLite3 database tables (*.rsk)
1. check date times
1. convert binary data (*downloads* table) to millivolt 
1. apply basic calibration parameters
1. apply temperature compensation for pressure


## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jkennel/rsk")
```

## Example (reading a 1 GB file)


```{r}

library(rsk)
library(oce)
fn = "../../r_scratch/c2 081870_20240501_1603.rsk"
# this reads in the data
system.time(rbr_rsk <- Rsk$new(file_name = fn, raw = TRUE))
system.time(rbr_rsk <- Rsk$new(file_name = fn, raw = FALSE))
system.time(rbr_oce <- oce::read.rsk(file = fn))
```


##  Data
The data is stored in a single *data.table* in wide format. *raw* refers to the millivolt measurements. For newer duets, temperature is measured onboard and at the sensor tip. *pressure_dbar_comp* refers to the final temperature compensated pressure.

```{r}
rbr_rsk$data
```


##  Plot of channels

```{r, eval = FALSE}
rbr_rsk$glance()
```

